HBCC - ACC-Nirmala - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-27 cmc-rnaseq-de/HBCC_ACC-Nirmala_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix covars

# Get RNASeq QCmetadata
METADATA_QC_ACC_ID = 'syn16816488' 
ALL_USED_IDs = METADATA_QC_ACC_ID
metadata = downloadFile_version(METADATA_QC_ACC_ID, version = 16) %>%
  dplyr::select(`Individual_ID`, Institution, `Reported_Gender`, Sex, Ethnicity, ageOfDeath, `PMI_(in_hours)`, Dx, 
                Sample_RNA_ID, one_of('Cohort',
                                      'rnaSeq_isolation:RIN',
                                      'rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:RNA_Isolation_Batch', 'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned',
                                      'rnaSeq_report:Transcripts_Detected')) %>% 
  dplyr::filter(Institution %in% c("NIMH-HBCC")) %>% 
  dplyr::filter(`rnaSeq_dissection:Brain_Region` %in% c("ACC")) %>% 
  dplyr::filter(Cohort %in% c("NIMH-HBCC-5"))

@@

### Data preprocessing
```{r preprocess.data}
# Merge metadata
METADATA = metadata %>%
  dplyr::left_join(GENOTYPE) %>% 
  dplyr::rename(Region = `rnaSeq_dissection:Brain_Region`,
                PMI = `PMI_(in_hours)`,
                RIN = `rnaSeq_isolation:RIN`, 
                ReportExclude = `rnaSeq_report:Exclude?`,
                GenotypeExclude = `SNP_report:Exclude?`,
                SampleID = Sample_RNA_ID,
                LibraryBatch = `rnaSeq_report:Library_Batch`,
                IsolationBatch = `rnaSeq_report:RNA_Isolation_Batch`,
                RibozeroBatch = `rnaSeq_report:Ribozero_Batch`,
                MappedReads = `rnaSeq_report:Mapped_Reads`,
                IntragenicRate = `rnaSeq_report:Intragenic_Rate`, IntronicRate = `rnaSeq_report:Intronic_Rate`, 
                IntergenicRate = `rnaSeq_report:Intergenic_Rate`, GenesDetected = `rnaSeq_report:Genes_Detected`,
                ExpProfEfficiency = `rnaSeq_report:Expression_Profiling_Efficiency`, rRNARate = `rnaSeq_report:rRNA_Rate`,
                TotalReads = `rnaSeq_report:Total_Reads`, AlignmentRate = `rnaSeq_report:Percent_Aligned`, TranscriptsDetected = `rnaSeq_report:Transcripts_Detected`) %>%
  dplyr::select(SampleID, Individual_ID, Institution, Reported_Gender,Sex, Ethnicity, ageOfDeath, PMI, Dx, 
                RIN, ReportExclude, GenotypeExclude, EV.1, EV.2, EV.3, EV.4, EV.5,
                LibraryBatch, FlowcellBatch, RibozeroBatch, MappedReads, TotalReads, GenesDetected, AlignmentRate,
                IntragenicRate, IntergenicRate, IntronicRate, ExpProfEfficiency, rRNARate, TranscriptsDetected) %>%
  dplyr::mutate(Dx = forcats::fct_recode(Dx, Other = "BP", Control = "Control", SCZ = "SCZ"))

>>>>

# Get RNASeq QCmetadata
METADATA_QC_ACC_ID = 'syn16816488' 
ALL_USED_IDs = METADATA_QC_ACC_ID
metadata = downloadFile_version(METADATA_QC_ACC_ID, version = 16) %>%
  dplyr::select(`Individual_ID`, Institution, `Reported_Gender`, Sex, Ethnicity, ageOfDeath, `PMI_(in_hours)`, Dx, 
                Sample_RNA_ID, one_of('Cohort',
                                      'rnaSeq_isolation:RIN',
                                      'rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_isolation:RNA_Isolation_Batch', 'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned',
                                      'rnaSeq_report:Transcripts_Detected')) %>% 
  dplyr::filter(Institution %in% c("NIMH-HBCC")) %>% 
  dplyr::filter(`rnaSeq_dissection:Brain_Region` %in% c("ACC")) %>% 
  dplyr::filter(Cohort %in% c("NIMH-HBCC-5"))

@@

### Data preprocessing
```{r preprocess.data}
# Merge metadata
METADATA = metadata %>%
  dplyr::left_join(GENOTYPE) %>% 
  dplyr::rename(Region = `rnaSeq_dissection:Brain_Region`,
                PMI = `PMI_(in_hours)`,
                RIN = `rnaSeq_isolation:RIN`, 
                ReportExclude = `rnaSeq_report:Exclude?`,
                GenotypeExclude = `SNP_report:Exclude?`,
                SampleID = Sample_RNA_ID,
                LibraryBatch = `rnaSeq_report:Library_Batch`,
                IsolationBatch = `rnaSeq_isolation:RNA_Isolation_Batch`,
                RibozeroBatch = `rnaSeq_report:Ribozero_Batch`,
                MappedReads = `rnaSeq_report:Mapped_Reads`,
                IntragenicRate = `rnaSeq_report:Intragenic_Rate`, IntronicRate = `rnaSeq_report:Intronic_Rate`, 
                IntergenicRate = `rnaSeq_report:Intergenic_Rate`, GenesDetected = `rnaSeq_report:Genes_Detected`,
                ExpProfEfficiency = `rnaSeq_report:Expression_Profiling_Efficiency`, rRNARate = `rnaSeq_report:rRNA_Rate`,
                TotalReads = `rnaSeq_report:Total_Reads`, AlignmentRate = `rnaSeq_report:Percent_Aligned`, TranscriptsDetected = `rnaSeq_report:Transcripts_Detected`) %>%
  dplyr::select(SampleID, Individual_ID, Institution, Reported_Gender,Sex, Ethnicity, ageOfDeath, PMI, Dx, 
                RIN, ReportExclude, GenotypeExclude, EV.1, EV.2, EV.3, EV.4, EV.5,
                LibraryBatch, IsolationBatch, RibozeroBatch, MappedReads, TotalReads, GenesDetected, AlignmentRate,
                IntragenicRate, IntergenicRate, IntronicRate, ExpProfEfficiency, rRNARate, TranscriptsDetected) %>%
  dplyr::mutate(Dx = forcats::fct_recode(Dx, Other = "BP", Control = "Control", SCZ = "SCZ"))
